---
title: "Messing around with the tweets"
author: "Nicolas Restrepo"
date: "February 18, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Messing around with the tweets

```{r}

library(tidyverse)
library(rebus)
library(stringi)
library(lubridate)
library(tidytext)

theme_set(theme_light())
```

```{r}

# Load the data 

tweets <- readRDS("~/R_Documents/conversion-narratives/walkaway_tweets.rds")
```

I begin by looking at when the tweets have been posted 

```{r}

# Date of tweets 

tweets %>% 
  count(date = as.Date(created_at)) %>% 
  ggplot(aes(x = date, y = n)) + 
  geom_line() + 
  expand_limits(y = 0 )
```

Users with the most tweets? 

```{r}

tweets %>%  
  count(screen_name, sort = TRUE ) %>% 
  head(12) %>% 
  mutate(screen_name = reorder(screen_name, n)) %>% 
  ggplot(aes(screen_name, n)) + 
  geom_col() + 
  coord_flip()


```

Maybe worth checking the tweets by these users. 

What about retweets? 

```{r}

tweets %>% 
  arrange(desc(retweet_count)) %>%  
  select(screen_name, text, retweet_count) %>% 
  view()
```

So this is interesting because most of the most "impactful" tweets haven't been by the people who have used the hashtag the most. 

What if we take both things into account? 

```{r}

tweets %>% 
  group_by(screen_name) %>% 
  summarize(tweets = n(), 
            retweets = sum(retweet_count)) %>% 
  arrange(desc(tweets)) %>% 
  arrange(desc(retweets))
```

Wildly different picture. It seems the top three users here are quite impactful. 

What about fave / retween ratio 

```{r}

tweets %>% 
  select(screen_name, text, retweet_count, favorite_count) %>%  
  mutate(ratio = (favorite_count + 1) / (retweet_count + 1)) %>%  
  arrange(desc(ratio))

```

Worth looking into these top tweets. Are they particularly problematic and/or offensive? 

I am going to begin to think about the content of the tweets. 

```{r}

# fewer columns 

tweet_words <- tweets %>% 
  select(screen_name, text, retweet_count, favorite_count, created_at) %>%  
  unnest_tokens(word, text, token = "tweets") %>%  # this makes sure keep hashtags and @s 
  anti_join(stop_words, by = "word")  %>% # super handy dataset from the tidytext package 
  filter(word != "#walkaway")

# Plot most common words 

tweet_words %>%  
  count(word, sort = TRUE ) %>% 
  head(16) %>% 
  mutate(word = reorder(word, n)) %>% 
  ggplot(aes(word, n)) + 
  geom_col() + 
  coord_flip()

```

This just seems like another propaganda campaign by rightwing bots

We could check at which words had an impact by looking whether they were retweeted or liked

```{r}

# Distribution of retweets 

tweet_words %>%  
  ggplot(aes(retweet_count + 1)) + 
  geom_histogram() + 
  scale_x_log10()

# Because it's so skewed we cannot use average or median 

tweet_words %>%  
  group_by(word) %>% 
  summarise(n = n(), 
            avg_retweets = exp(mean(log(retweet_count + 1))) - 1, 
            avg_favorites = exp(mean(log(favorite_count + 1))) -1) %>% 
  filter(n >= 30) %>%  
  arrange(desc(avg_retweets)) %>%  
  head(n = 20)

```

Again, we mostly see hashtags up there on the list. @realpersonpltcs is quite impactful. 

We can create a tf_idf for each day to see how they have changed 

```{r}

# create specific day 

tweet_words <- tweet_words %>% 
  mutate( day = round_date(created_at, "day")) 

# Which words are more specific to particular days 

tweet_words %>% 
  count(word, day) %>% 
  bind_tf_idf(word, day, n) %>% 
  arrange(desc(tf_idf)) %>% 
  group_by(day) %>% 
  top_n(1, tf_idf) %>% 
  arrange(day) %>% 
  print()

# This is not suuuper helpful 

# Although it is interesting to see that most of them are handles 
```

